\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
They are scared to hell but after few minutes they see jaguar running towrads the other part of the forest. They finally feel a little relaxed but soon they hear something weird noises behind them. John being the adventurous and curious one decides to have a peek. As both Jay and Kate are scared of the jaguar they just go behind John. They reach a cave are left awestruck. They feel that what is infront of them looks something like a fantasy for instance, Chronicles Of Narnia. Whether it’s hiding in the back of a wardrobe, or through a door in the wall, or straddling invisible lines in reality, portals lurk among us, and transport us to impossible worlds. Well, they haven't seen anything like that before .Without giving a second thought, John and Jay make the leap into the unknown, fueled by number of emotions but mainly curiosity and wonder. Kate does not want to take the risk but she can not leave Jay alone and the fact that she is still lost and without Jay she would not be able to find her way back home, she jumps in too. They have no clue what lies on this side of the world. What lies on the other side is where the real story starts. They finally get a chance to be someone else, or become who they've always wanted to be or even just to live away form who they were. John, Jay and Kate hold their seats for a new experience and wonder whats ahead of them and are surprised how a normal hike became an adventure for Jay, Kate and John.

{\fontfamily{lmr}\selectfont
**
This is a whole new world full of magic and danger, dimension-hopping rings, kings and queens, lion kings, and everything talking. This new world will be a part of Adventure story Part 2. Stay connected pals and explore the world of magic with Jay and Kate.
}
\end{document}
